Notes on Prediction Types

### 2011-10-14 docs/pert_notes/pert.tex
add note about what happens when use_tfromp = T and we try different predicting T to the edges

\noindent Note: the various {\tt enthalpy\_pred\_type}s have only been
extensively tested with {\tt species\_pred\_type = 1}.

>>>>

\noindent Note that the various {\tt enthalpy\_pred\_type}s have only been
extensively tested with {\tt species\_pred\_type = 1}.

Finally, when \maestro\ is run with {\tt use\_tfromp = T}, the
temperature is derived from the density, basestate pressure ($p_0$),
and $X_k$.  When run with reactions or external heating, {\tt
  react\_state} updates the temperature after the reaction/heating
term is computed.  In {\tt use\_tfromp = T} mode, the temperature will
not see the heat release, since the enthalpy does not feed in.  Only
after the hydro update does the temperature gain the effects of the
heat release due to the adjustment of the density (which in turn sees
it through the velocity field and $S$).  As a result, the {\tt
  enthalpy\_pred\_type}s that predict temperature to the interface
({\tt predict\_T\_then\_rhoprime} and {\tt predict\_T\_then\_h}) will
not work.  \maestro\ will abort if the code is run with this
combination of parameters.
